---
title: "Draft"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# load data
raw.questions <- read.csv("June 10-July 12, 2015 - Gaming, Jobs and Broadband_revised by Mei.csv",nrow=1)
raw.data <- read.csv("June 10-July 12, 2015 - Gaming, Jobs and Broadband_revised by Mei.csv",skip=2,header=FALSE) 
#raw.data$age <- as.numeric(raw.data$age) # convert all the variable to factors except for age
names(raw.data) <-names(raw.questions)

library(pscl) # for pesudo r square in logit model

library(dplyr)
# turn data into tbl_df by using dplyr
raw.data<-tbl_df(raw.data)

```


# Question 1. Whether people who use social media to find a job tend to use online dating website?
Thinking about social media sites like Facebook, Twitter or LinkedIn… Have you ever
a.	Used social media to look for or research a job
b.	Applied for a job that you found out about on social media
c.	Used social media to let your friends know about a job that was available at your place of employment
```{r}
tab <- raw.data[,c("date1a","snsjob1a","snsjob1b","snsjob1c")]
tab <- tab %>% filter(date1a==1|date1a==2,snsjob1a==1|snsjob1a==2,snsjob1a==1|snsjob1a==2,snsjob1b==1|snsjob1b==2,snsjob1c==1|snsjob1c==2)
tab$date1a[which(tab["date1a"]==2)] <- 0
chisq.test(table(tab$date1a,tab$snsjob1b))

# chi-square test of each two variable in tab
p.val=matrix(nrow=ncol(tab),ncol=ncol(tab))
for (i in 1:ncol(tab)){
  for (j in 1:ncol(tab)){
    tab2<-data.frame(tab[,i],tab[,j])
    table.test <- table(tab2)
    p.val[i,j] <- chisq.test(table.test)$p.value
  }
}

model_social<-glm(factor(date1a)~factor(snsjob1a),data=tab,family = "binomial")
summary(model_social)
pR2(model.social) 

#test whether there is overdispersion
fitod<-glm(factor(date1a)~factor(snsjob1a),data=tab,family = "quasibinomial")
pchisq(summary(fitod)$dispersion*model.social$df.residual,model.social$df.residual,lower=F)

model.social<-glm(factor(date1a)~factor(snsjob1b),data=tab,family = "binomial")
summary(model.social)
pR2(model.social) # pesudo r square

```
If change the dependent variable to date2a(online dating app), the snsjob1a is also significant, so people using social media to look for or research a job tend to go for online dating through Internet or smartphone app.


# Question 2. cellphone and online dating app
Do you ever use your cell phone to
a.	Participate in a video call or video chat {modified Master CELLVCHT}
b.	Buy a product online, such as books, music, toys or clothing {New}
c.	Get directions, recommendations, or other information related to your location

```{r}
cellphone.tab <- raw.data[,c("date2a","q5a","q5b","q5c")]
cellphone.tab <- filter(cellphone.table,date2a==1|date2a==2,q5a==1|q5a==2,q5b==1|q5b==2,q5c==1|q5c==2)
cellphone.tab$date2a[which(cellphone.tab["date2a"]==2)] <- 0

p.val2=matrix(nrow=ncol(cellphone.tab),ncol=ncol(cellphone.tab))
for (i in 1:ncol(cellphone.tab)){
  for (j in 1:ncol(cellphone.tab)){
    tab2<-data.frame(cellphone.tab[,i],cellphone.tab[,j])
    table.test <- table(tab2)
    p.val2[i,j] <- chisq.test(table.test)$p.value
  }
}

model.cellphone<-glm(date2a~q5a+q5b+q5c,data=cellphone.table,family = "binomial")
summary(model.cellphone)
# delete non-significant variable
model.cellphone<-glm(date2a~q5a+q5b,data=cellphone.table,family = "binomial")
summary(model.cellphone)
pR2(model.cellphone)

#test whether there is an overdispersion
fitod<-glm(date2a~q5a+q5b,data=cellphone.table,family = "quasibinomial")
pchisq(summary(fitod)$dispersion*model.cellphone$df.residual,model.cellphone$df.residual,lower=F)


```
Estimated parameters of q5a and q5b are significant, so there is larger probability that people who like to chatting online or shopping online would like to choose online dating app.

Since the p-value is 0.4703885 >0.05, we fail to reject the hull hypothesis that the Dispersion parameter equals to 1, which means there is no overdispersion in this model.

# Question 3: whether people who use online resource to find a job tend to use online dating website
People may use many different resources when looking for a job. Thinking of your MOST RECENT job search, please tell me if you used any of the following resources. 

d.Resources or information you found online

```{r}
resource.table <- raw.data[,c("date1a","job5d")]
resource.table <- filter(resource.table,date1a==1|date1a==2,job5d==1|job5d==2)
#resource_table$date1a[which(resource_table["date1a"]==2)] <- 0
chitest.table<-table(resource.table)
chisq.test(chitest.table)

```
The hull hypothesis whether the people using online resource to find a job is independent of using online dating website at .05 significance level.The p-value is 0.4271 > 0.05 and we fail to reject the hypothesis, so people using online resource to find a job is independent of using online dating website.


# Question 4: Influece of Demographic Data, habbits of job searching and Internet using on whether to use online dating app

```{r}
job.table <- raw.data[,c('date2a','q5a','q5b','snsjob1a','age','sex','educ2','marital','party','inc','race','emplnw','ideo')]
job.table <- filter(job.table,date2a==1|date2a==2,q5a==1|q5a==2,q5b==1|q5b==2,snsjob1a==1|snsjob1a==2,age<97,inc!=98,inc!=99,marital!=8,marital!=9,educ2!=98,educ2!=99,party!=8,party!=9,race!=9,race!=8,emplnw!=98,emplnw!=99)
job.table$date2a[which(job.table["date2a"]==2)] <- 0

model.logit <- glm(factor(date2a)~factor(q5a)+factor(q5b)+factor(snsjob1a)+age+factor(sex)+factor(educ2)+factor(marital)+factor(party)+factor(inc)+factor(race)+factor(emplnw),data=job.table,family = "binomial")
summary(model.logit)

model.logit2 <- glm(date2a~q5b+snsjob1a+marital,data=job.table,family = "binomial")
summary(model.logit2)
pR2(model.logit2)

#test whether there is overdispersion
fitod<-glm(date2a~q5b+snsjob1a+marital,data=job.table,family = "quasibinomial")
pchisq(summary(fitod)$dispersion*model.logit2$df.residual,model.logit2$df.residual,lower=F)

```
snsjob1a: Used social media to look for or research a job
q5bb: Buy a product online, such as books, music, toys or clothing
marital: mariage status
The above three variables are significant.

# Question 5.What kind of people like to choose online dating (cluster)
(still need time to work on this)

```{r}
#question data4c is reversd
#for (i in 1:nrow(raw.data)){
#  if (raw.data[i,"date4c"]==2 | raw.data[i,"date4c"]==1){
#    raw.data[i,"date4c"]= abs(raw.data[i,"date4c"]-3)
#  }
#}

#datingpeople<-raw.data %>% filter((eminuse==1|intmob==1)&smart1==1)
#clusterdata<-select(datingpeople,date1a,date4b,date4c,date4d,date4e,date4f)
#library(ClustOfVar)
#for(i in ncol(clusterdata)){
#  clusterdata[,i]<-as.numeric(clusterdata[,i])
#}
#km.out<-kmeans(clusterdata,2)

```

