---
title: "Report Structure"
author: "Mei Sheng"
date: "10/11/2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Assuming we are a company focused on online dating app and website, we want to make some business strategy and decision based on the data we have collected.
Our main purpose of this report includes 3 parts:
# 
1. Newcutomer  Acquisition
How does our origial user look like? demographic analysis (Lawrence & Marnelia) (Yerik)
How can we find new sorucres of growth? 
*Eg. the relationship between people's preference or habits of cellphone and Internet in daily life and online dating preference  (Mei & Zhewei) 

Find our target users (protential users who are not against online dating but haven't use it before) (Lawrence & Marnelia)
cluster?? if cluster doesn't work, we can do the following analysis:
according to their attitude on online dating , we can find people who choose agreee more than 3 out of 6 questions as our protential user and analyse their behavior 

2. Marketing strategy
According to the characteristic of protential users, make our marketing strategy ( where to advertise: social media, online shopping website...) 
We analyze the following relationship based on the available data in our dataset:
                                       
(1) relationship between job searching preference and online dating preference  (Mei & Zhewei)  
(2) relationship between gaming and online dating preference (Yerik & Virat)

3. Monetization
how to tell advertisers that our users are their target audience
(1) app users' employment status => more potential buyer (Mei & Zhewei) 
(2) relationship between jobsearching and online dating ( if we can use online dating to predict users' behavior of job searching) (Mei & Zhewei) 



```{r}

```

